Alleviating Topology Mismatch in Distributed Overlay Networks: A Survey

### 2014-01-27 background.tex
2012.12.23 (Mema) Text reworked.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (P2P) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first P2P file-sharing systems introduced the \emph{servent}
concept \cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the twofold role of a node participating in the P2P
network. Such server-less systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. While certain
undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
the distribution of illegal content and other \emph{socio-technical}
issues \cite{hughes_socp2p_2008}, have arisen, peer-to-peer systems have
continued to gain popularity mainly because they have successfully supported
popular applications (i.e. file-sharing) amongst vast numbers of participating
users.

@@

Designers of \emph{centralized} architectures (see
Figure~\ref{figure:p2p-archs:centralized}) were the first to recognize that
requests for resources (e.g. CPU cycles or popular content) need not be sent to
a dedicated server but instead could be handled by the many hosts that already
posses the resources. The downside of this approach is that it requires a
centralized searching facility which becomes a single point of failure, a
scalability bottleneck, and a target of malicious attacks (e.g.,
\emph{Denial-of-Service (DoS) attacks}).

The most successful incarnation of the centralized approach is the file-sharing
application \emph{Napster}\cite{napster}. Napster maintained a \emph{central
index server} based on file lists provided by participating peers. The central
index server was queried by users and it returned pointers to the actual
content. Thus, by centralizing search while distributing downloads,  Napster
achieved a highly functional design that, at its height, attrated 26 million
users sharing approximately 80 million songs\cite{jmm_naptopusage_2001}.
Napter's  centralized nature was what ultimately brought it down after Recording
Industry Association of America (RIAA) filed a lawsuit for copyright infringemnt
of the intellectual property of artists whose music was distributed by the
Napster application. RIAA was able to point to the centralized indexing
component of Napster as the entity resposible for illegal song-trading.

@@

To improve search scope and scalability and to lighten network load, 
unstructured systems evolved into ``hierarchical'' systems that dynamically
assign indexing functions to special peers, called \emph{ultra-peers}  or
\emph{super-peers} (see
Figure~\ref{figure:p2p-archs:unstructured-hierarchical}). Peers with reliable
network connections and/or high compute power became ultra/super-peers
facilitating less powerful peers (called \emph{leaf-nodes}) to find resources of
interest. Well-known examples of these hierarchical unstructured systems include
Gnutella v.0.6/Limewire~\cite{gnutella}, KaZaA~\cite{kazaa} and
Skype~\cite{skype}. While the hierarchical approach relieves network pressure as
search queries are flooded over a much smaller subset of peers (the
ultra/super-peers), the disadvantages of reduced search scope and inability to
locate rare resources efficiently remain.

To fully address the disadvantages of decentralized unstructured approaches,
\emph{decentralized structured} schemes have been proposed (see
Figure~\ref{figure:p2p-archs:structured}). The key goal of these systems is to
provide a self-organizing infrastructure for large-scale P2P applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
They implement a \emph{Distributed Hash Table (DHT)} that maps objects to nodes
through a deterministic mechanism. The DHT provides a guaranteed bound on the
number of overlay routing hops that have to be taken to locate a resource, even
in the case when only a single copy exists in the system.  This means
$O \left( log n \right)$ hops, compared to unstructured networks that require
$O \left( n \right)$ to reliably locate any object. Unfortunately this
efficiency does not come without cost. Structured overlays can only support
exact-match queries (i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. This means
that unstructured overlays can support more versatile resource location queries
such as keyword and partial matching searches. Several popular file-sharing
peer-to-peer applications have been based on DHTs including
Overnet/eDonkey~\cite{overnet}, Kademlia/Kad
Network~\cite{maymounkov_kademlia_2002}, some flavors of
BitTorrent~\cite{c_bittorrent_2003}, and many more.  Moreover, DHTs have sparked
a flurry of research activity and development for a large range of applications:
from distributed search engines to event notification infrastructures to
cloud-based platforms. We cite several examples in Section~\ref{section:intro}.

\begin{figure}[ht]
\centering
\subfigure[Centralized (SETI@Home or Napster). Peers query the centralized
entity (dotted lines) and then establish the connection to the data source.] {
  \includegraphics[scale=0.25]{img/pdf/centralized.pdf}
  \label{figure:p2p-archs:centralized}
}\qquad\qquad
\subfigure[Fully unstructured (Gnutella v.0.4). Data is distributed randomly,
the topology is also random and all participants are equal.] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructured-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured (Gnutella v.0.6 or FastTrack). Certain
peers (bigger circles) shoulder specific responsibilities (e.g., data
indexing).] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad\qquad
\subfigure[Structured (Chord and Kademlia). Peers and data are placed into the
overlay in a deterministic manner.] {
  \includegraphics[scale=0.25]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various peer-to-peer architectures.}
\label{figure:p2p-archs}
\end{figure}

@@

One of the major issues that defines the efficiency of an overlay network is the
mapping of the overlay structure to the underlying infrastructure. Remember, in
Figure~\ref{figure:overlay} nodes $A$ and $B$ are on the same local network,
while $C$ and $D$ are in different networks. The top layer represents the
overlay interconnection formed by these nodes at a higher level. Link
connections there, can change as needed by the running environment, without any
particular constraint by the underlying physical topology. Let's have a closer
look with the help of a simple example. Assume nodes $A$, $B$, $C$ and $D$ are
connected through the physical network shown in Figure~\ref{figure:phys}, where
the network costs are given in milliseconds, and peer $A$ sends a message to
peer $D$.

@@

If these peers participate in an overlay network according to one of the setups
of Figure~\ref{figure:overlay-confs}, then users will experience different
performances. In the overlay depicted in Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. The total cost of the first sequence is $45 ms$, while the second yields a
mere $15 ms$. Therefore, we can conclude that the second overlay is more
congruent with the underlying physical network than the first one and, thus, is
more efficient.

@@

Ideally, an overlay network should be constructed to achieve an optimal 
mapping among the overlay paths and the underlying network links to avoid
inefficient states were redundant physical resources are utilised for the
operation of a link on the overlay. The problem of constructing an optimal
overlay is referred to as the \emph{topology mismatch problem}, and is formally
defined as follows:
\begin{definition}
Let $V = \{v_1, ..., v_n\}$ be a set of points denoting the network nodes,
$\{v_i, v_j\} \in E$ be the set of unicast distances between nodes $v_i$ and
$v_j$, $G=(V,E)$ be a complete distance graph over $V$. The topology mismatch
problem is to construct a minimal spanning tree, where node degree is
restricted to a constant ($k\geq 2$) by the bandwidth of each node $v_i$.
\end{definition}

Early incarnations of the overlay protocols did not make use of the optimal
mapping with the underlying network topology. Gnutella, for example, is
considered far from scalable \cite{ritter_gnucantscale_2001} because every peer
chooses its neighbors in the overlay without any knowledge of the underlying
network, resulting in a mismatch between the two topologies. Queries may be
flooded over multiple paths merging in one peer while one of the paths would
have been enough. Moreover, peers may forward the same message to each other
before they receive the query messages from each other.
\cite{matei_mapgnutella_2002} showed that, even when 95\% of any two nodes are
less than 7 hops away from each other, a \emph{flooding-based} algorithm, like
the one used by Gnutella, can generate 330TB/month in a 50.000 node network. A
topology mismatch can thus have a serious effect on Internet router performance.

Similar problems are observed in decentralized structured schemes as well.
Typically, node IDs are assigned \emph{randomly}, resulting in excellent load
balancing, scalability, and robustness for the overlay. Unfortunately, this
randomness has a negative impact on the \emph{routing locality} of the network.
This means that even though the target node can be reached with logarithmic
overlay hops, the distance traveled in the underlying network, during the
overlay routing process, can be far from optimal.  The ratio of the actual IP
network distance a query travels to reach an object of interest (via overlay
routing) to the minimal IP network distance to that object (i.e. through IP) is
known as \emph{stretch} or \emph{Relative Delay Penalty (RDP)} \cite{CRZ2000}.

@@

Over the past several years, researchers have proposed and studied an extensive
array of heuristic solutions to the topology mismatch problem. The purpose of
this survey is to gather and organize the extensive knowledge that has been
produced. We hope to assist the reader to understand the different approaches
that have been proposed to tackle the topology mismatch problem. In order to do
so, we dedicate a discussion subsection after the presentation of the algorithms
for both unstructured and structured architectures. This section offers:
\begin{inparaenum}[\itshape i\upshape)]
  \item further discussion that can help the reader identify, through
a taxonomy, the pluses and minuses in the preceding material,
  \item a comprehensive tabular organization of the key-point information, and
  \item an attempt to give a pictorial comparison of the relative performance of
the algorithms.
\end{inparaenum}

In discussion we offer the reader a deeper insight for the observations that
pushed research toward some direction. Thus, we try to categorize these
approaches so that we can organize directions making them comprehensible
and helping the reader build critical thinking on the advantages and
disadvantages of each approach.

Tables provide a one-stop-shop overview for the algorithms so that can be a
helpful tool both as a companion during reading the survey and a reference for
future use.

Pictorial comparison consists of bar charts that give a relative feeling of the
performance of the various algorithms, discussed in the corresponding section,
in
terms of \emph{efficiency}, \emph{overhead} and \emph{scalability}; three
important characteristics for every distributed algorithm. For all we used a
coarse grained, three level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}. Each category has its own
interpretation of the above literal values. Efficiency means how well the
algorithm performs its search and topology adaptation functions, without
effecting other characteristics of the networks (e.g. BitTorrent's optimal
download performance). To name few, we assume that efficiency is
negatively effected when an algorithm reduces the search scope. Moreover, the
minimum-spanning-tree-based techniques have slow convergence speed in topology
adaptation or the high clustering impacts load balancing and constrains search
scope (or at least increases search satisfaction time), all reducing overall
efficiency. With overhead we track the cost to compute and communicate peer
join, message forwarding and topology maintenance. For example when exchanging
cost tables only along neighbors the traffic generated can be considered
trivial. Also duplicates minimization is a plus and lazy or heart-beat-based
overlay control mechanisms impose different amount of stress to the network.
Nevertheless, caching/replication helps reducing the overall overhead by
constraining the query from spreading too much. Low convergence speed of
minimum-spanning-tree-based approaches, we mentioned above for efficiency,
results also in additional computational and communicational overhead.
% TODO: We check
% complexity in the asymptotic sense, using \emph{Big O} notation % in order to
% check how the algorithm responds t. We take into account topology % creation and
% topology maintenance...
% TODO: HELP NEEDED!
With scalability we check the systems behavior with respect to the number of
participating peers. Low, medium and high scalability can be generally
considered in the order of hundreds, tenths of thousands and millions,
respectively. Fully distributed approaches is a plus (no system-centric entities
involved, no need for global knowledge) and topology adaptation strengthens
scalability in highly dynamic environments. Reduced search scope, on the other
hand, penalizes the scalability since the more peers coming in the network the
more potentially unsatisfied queries will there be. Furthermore, clock
synchronization is a limiting factor to scalability of a distributed system.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (P2P) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first P2P file-sharing systems introduced the \emph{servent}
concept \cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the twofold role of a node participating in the P2P
network. Such server-less systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. While certain
undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
the distribution of illegal content and other \emph{socio-technical}
issues \cite{hughes_socp2p_2008}, have arisen, peer-to-peer systems have
continued to gain popularity throughout the years primarily because they have successfully supported
popular applications (i.e. file-sharing) amongst vast numbers of participating
users.

@@

Designers of \emph{centralized} architectures (see
Figure~\ref{figure:p2p-archs:centralized}) were the first to recognize that
requests for resources (e.g. CPU cycles or popular content) need not be sent to
a dedicated server but instead could be handled by the many hosts that already
posess the resources. The downside of this approach is that it requires a
centralized searching facility which becomes a single point of failure, a
scalability bottleneck, and a target of malicious attacks (e.g.,
\emph{Denial-of-Service (DoS) attacks}).

The most successful incarnation of the centralized approach is the file-sharing
application \emph{Napster}\cite{napster}. Napster maintained a \emph{central
index server} based on file lists provided by participating peers. The central
index server was queried by users and it returned pointers to the actual
content. Thus, by centralizing search while distributing downloads,  Napster
achieved a highly functional design that, at its height, attracted 26 million
users sharing approximately 80 million songs\cite{jmm_naptopusage_2001}.
Napter's  centralized nature was what ultimately brought it down after Recording
Industry Association of America (RIAA) filed a lawsuit for copyright infringemnt
of the intellectual property of artists whose music was distributed by the
Napster application. RIAA was able to point to the centralized indexing
component of Napster as the entity resposible for illegal song-trading.

@@

To improve search scope and scalability and to lighten network load, 
unstructured systems evolved into ``hierarchical'' systems that dynamically
assign indexing functions to special peers, called \emph{ultra-peers}  or
\emph{super-peers} (see
Figure~\ref{figure:p2p-archs:unstructured-hierarchical}). Peers with reliable
network connections and/or high compute power became ultra/super-peers
facilitating less powerful peers (called \emph{leaf-nodes}) to find resources of
interest. Well-known examples of these hierarchical unstructured systems include
Gnutella v.0.6/Limewire~\cite{gnutella}, KaZaA~\cite{kazaa} and
Skype~\cite{skype}. While the hierarchical approach relieves network pressure as
search queries are flooded over a much smaller subset of peers (the
ultra/super-peers), the disadvantages of reduced search scope and inability to
locate rare resources remain.

To fully address the disadvantages of decentralized unstructured approaches,
\emph{decentralized structured} schemes have been proposed (see
Figure~\ref{figure:p2p-archs:structured}). The key goal of these systems is to
provide a self-organizing infrastructure for large-scale P2P applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
They implement a \emph{Distributed Hash Table (DHT)} that maps objects to nodes
through a deterministic mechanism. The DHT provides a guaranteed bound on the
number of overlay routing hops that have to be crossed to locate a resource, even
in the case when only a single copy exists in the system.  This requires
$O \left( log n \right)$ hops, compared to unstructured networks that require
$O \left( n \right)$ to reliably locate any object. Unfortunately this
efficiency does not come without cost. Structured overlays can only support
exact-match queries (i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. This means
that unstructured overlays can support more versatile resource location queries
such as keyword and partial matching searches. Several popular file-sharing
peer-to-peer applications have been based on DHTs including
Overnet/eDonkey~\cite{overnet}, Kademlia/Kad
Network~\cite{maymounkov_kademlia_2002}, some flavors of
BitTorrent~\cite{c_bittorrent_2003}, and many more.  Moreover, DHTs have sparked
a flurry of research activity and development for a large range of applications:
from distributed search engines to event notification infrastructures to
cloud-based platforms. We cite several examples in Section~\ref{section:intro}.

\begin{figure}[ht]
\centering
\subfigure[Centralized (SETI@Home or Napster). Peers query the centralized
entity (dotted lines) and then establish the connection to the data source.] {
  \includegraphics[scale=0.25]{img/pdf/centralized.pdf}
  \label{figure:p2p-archs:centralized}
}\qquad\qquad
\subfigure[Fully unstructured (Gnutella v.0.4). Data is distributed randomly,
the topology is also random and all participants are equal.] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructured-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured (Gnutella v.0.6 or FastTrack). Certain
peers (bigger circles) shoulder specific responsibilities (e.g., data
indexing).] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad\qquad
\subfigure[Structured (Chord and Kademlia). Peers and data are placed in the
overlay in a deterministic manner.] {
  \includegraphics[scale=0.25]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various peer-to-peer architectures.}
\label{figure:p2p-archs}
\end{figure}

@@

One of the major issues that defines the efficiency of an overlay network is the
mapping of the overlay structure to the underlying infrastructure. Recall,, in
Figure~\ref{figure:overlay} nodes $A$ and $B$ are on the same local network,
while $C$ and $D$ are in different networks. The top layer represents the
overlay interconnection formed by these nodes at a higher level. Link
connections there, can change as needed by the running environment, without any
particular constraint by the underlying physical topology. Consider the following
example. 
Assume nodes $A$, $B$, $C$ and $D$ are
connected via the physical network shown in Figure~\ref{figure:phys}, where
the network costs are given in milliseconds, and peer $A$ sends a message to
peer $D$.

@@

Depending on the configuration of the overlay,
peers will experience different performance.
For example, in the overlay depicted in
Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. The total cost of the first sequence is $45 ms$, while the second yields a
mere $15 ms$. Therefore, we can conclude that the second overlay is more
congruent with the underlying physical network than the first one and, thus, is
more efficient.

@@

Ideally, an overlay network should be constructed to achieve an optimal 
mapping between the overlay paths and the underlying network links to avoid
inefficient states where redundant physical resources are utilised for the
operation of the same link in the overlay. The problem of constructing an optimal
overlay is referred to as the \emph{topology mismatch problem}, and is formally
defined as follows:
\begin{definition}
Let $V = \{v_1, ..., v_n\}$ be a set of points denoting the network nodes,
$\{v_i, v_j\} \in E$ be the set of unicast distances between nodes $v_i$ and
$v_j$, $G=(V,E)$ be a complete distance graph over $V$. The topology mismatch
problem is to construct a minimal spanning tree, where node degree is
restricted to a constant ($k\geq 2$) by the bandwidth of each node $v_i$.
\end{definition}

Early incarnations of the overlay protocols did not make use of the optimal
mapping with the underlying network topology. Gnutella, for example, is
considered far from scalable \cite{ritter_gnucantscale_2001} because every peer
chooses its neighbors in the overlay without any knowledge of the underlying
network, resulting in a mismatch between the two topologies. Queries may be
flooded over multiple paths merging in one peer while one of the paths would
suffice.  Moreover, peers may forward the same message to each other
before they receive the query messages from each other.
\cite{matei_mapgnutella_2002} showed that, even when 95\% of any two nodes are
less than 7 hops away from each other, a \emph{flooding-based} algorithm, like
the one used by Gnutella, can generate 330TB/month in a 50.000 node network. A
topology mismatch can thus have a serious effect on Internet router performance.

Similar problems are observed in decentralized structured schemes as well.
Typically, node IDs are assigned \emph{randomly}, resulting in excellent load
balancing, scalability, and robustness for the overlay. Unfortunately, this
randomness has a negative impact on the \emph{routing locality} of the network.
This means that even though the target node can be reached with a logarithmic
number of overlay hops, the distance traveled in the underlying network, during the
overlay routing process, can be far from optimal.  The ratio of the actual IP
network distance a query travels to reach an object of interest (via overlay
routing) to the minimal IP network distance to that object (i.e. through IP) is
known as \emph{stretch} or \emph{Relative Delay Penalty (RDP)} \cite{CRZ2000}.

@@

Over the past several years, researchers have proposed and studied an extensive
array of heuristic solutions to the topology mismatch problem. The purpose of
this survey is to gather and organize the extensive knowledge that has been
produced. We hope to assist the reader to understand the different approaches
that have been proposed to tackle the topology mismatch problem. In order to do
so, we dedicate a discussion subsection after the presentation of the algorithms
for both unstructured and structured architectures. This section offers:
\begin{inparaenum}[\itshape i\upshape)]
  \item further discussion that can help the reader identify, through
a taxonomy, the pluses and minuses  of the presented algorithms,
  \item a comprehensive tabular organization of the key-point information, and
  \item an attempt to give a pictorial comparison of the relative performance of
the algorithms.
\end{inparaenum}

We hope to offer the reader a deeper insight for the observations that
pushed research toward some direction. Thus, we try to categorize these
approaches so that we can organize directions making them comprehensible
and helping the reader build critical thinking on the advantages and
disadvantages of each approach.

Tables provide a one-stop-shop overview of the algorithms and serve as a 
tool both as a companion to the reader while reading the survey and a reference for
future use.

Pictorial comparison consists of bar charts that give a relative feeling of the
performance of the various algorithms, discussed in the corresponding section,
in
terms of \emph{efficiency}, \emph{overhead} and \emph{scalability}; three
important characteristics for every distributed algorithm. For each of these
criteria, we use a
coarse-grained, three-level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}. Each criterion has its own
interpretation of the above literal values. Efficiency means how well the
algorithm performs its search and topology adaptation functions, without
affecting other characteristics of the networks (e.g. BitTorrent's optimal
download performance). We assume that efficiency is
negatively effected when an algorithm reduces the search scope. 
%Moreover, the

%minimum-spanning-tree-based techniques have slow convergence speed in topology

%adaptation or the high clustering impacts load balancing and constrains search

%scope (or at least increases search satisfaction time), all reducing overall

%efficiency. 
For the overhead criterion, we track the cost to compute and communicate peer
join, message forwarding, and topology maintenance. For example, when exchanging
route tables only amongst neighbors, we consider the traffic generated to
be low.
%Also duplicates minimization is a plus and lazy or heart-beat-based
%overlay control mechanisms impose different amount of stress to the network.
%Nevertheless, caching/replication helps reducing the overall overhead by
%constraining the query from spreading too much. Low convergence speed of
%minimum-spanning-tree-based approaches, we mentioned above for efficiency,
%results also in additional computational and communicational overhead.
% TODO: We check
% complexity in the asymptotic sense, using \emph{Big O} notation % in order to
% check how the algorithm responds t. We take into account topology % creation and
% topology maintenance...
% TODO: HELP NEEDED!
For the scalability criterion, we consider system behavior with respect to the number of
participating peers. We consider systems with low, medium, and high scalability 
to mean they can support 
hundreds, tenths of thousands, and millions of nodes,
respectively. 
%Fully distributed approaches is a plus (no system-centric entities

%involved, no need for global knowledge) and topology adaptation strengthens

%scalability in highly dynamic environments. Reduced search scope, on the other

%hand, penalizes the scalability since the more peers coming in the network the

%more potentially unsatisfied queries will there be. Furthermore, clock

%synchronization is a limiting factor to scalability of a distributed system.

### 2014-01-27 conclusion.tex
2012.12.23 (Mema) Text reworked.

Peer-to-peer architecture has been in the center of research attention in the
last decade. Especially the decentralized unstructured genre exploits the
advantages of loose coupling and self organization of computing nodes to form
application-layer networks on top of the physical, best-effort infrastructure of
the Internet that exhibit interesting properties. Scalability problems arouse
quickly, though, because of the inefficient construction of this overlay that
was built with no concern for the underlying physical network that causes a
great deal of redundant traffic. The problem was identified by the research
community as the topology mismatch problem between the overlay and the
corresponding underlying physical network and a great deal of effort has been
set towards alleviating it. Some fruits of this effort have been gathered and
presented in this survey. Measurement of link cost through latency or RTT and
deletion of inefficient established connections are the key concepts of almost
all approaches. Others, manage to address the problem through hierarchical peer
clustering (e.g. best IP matching). Additionally, some protocols focus on
specific problems that furtherly arise, such as overlay partitioning, search
scope reduction or convergence speed, to name just a few. Another desire is to
form a protocol that could be applied to both decentralized unstructured and
decentralized structured networks. Unfortunately no approach has equally
addressed these problems in order to form a robust solution. So the field seems
to be, still, fertile for any, new, clever idea.

>>>>

Computer systems design is typically about juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured P2P networks, we find this
tussle-of-tradeoffs property to hold.  With regards to the three criteria 
we used (efficiency,
overhead, and scalability), we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by presenting 1) an
analysis of each of the solutions, including what distinguishes it from the
others and its advantages and disadvantages and 
2) a pictorial
comparison of how each solution fares compared with the others with regards
to efficiency, overhead, and scalability, we hope to have provided P2P
developers and researchers 
with enough perspective so that depending on the needs of their particular
application, they are able to select
amongst these surveyed solutions or propose a new solution of their own.

%Peer-to-peer architecture has been in the center of research attention in the
%advantages of loose coupling and self organization of computing nodes to form
%application-layer networks on top of the physical, best-effort infrastructure of
%the Internet that exhibit interesting properties. Scalability problems arouse
%quickly, though, because of the inefficient construction of this overlay that
%was built with no concern for the underlying physical network that causes a
%great deal of redundant traffic. The problem was identified by the research
%community as the topology mismatch problem between the overlay and the
%corresponding underlying physical network and a great deal of effort has been
%set towards alleviating it. Some fruits of this effort have been gathered and
%presented in this survey. Measurement of link cost through latency or RTT and
%deletion of inefficient established connections are the key concepts of almost
%all approaches. Others, manage to address the problem through hierarchical peer
%clustering (e.g. best IP matching). Additionally, some protocols focus on
%specific problems that furtherly arise, such as overlay partitioning, search
%scope reduction or convergence speed, to name just a few. Another desire is to
%form a protocol that could be applied to both decentralized unstructured and
%decentralized structured networks. Unfortunately no approach has equally
%addressed these problems in order to form a robust solution. So the field seems
%to be, still, fertile for any, new, clever idea.
